Cannibalism among the supermassive black holes

### 2018-10-06 paper.tex
Added 'dark matter' to section Overview of simulation

\subsection{Overview of simulation}
Our simulations focus on elliptical galaxies with central SMBHs. The galaxies were given a background potential based on the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.  The galaxies were evolved from $4 > z > 0$.  Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed, as described further below.

>>>>

\subsection{Overview of simulation}
Our simulations focus on elliptical galaxies with central SMBHs. The galaxies were given a dark matter background potential using the Stone-Ostriker profile (\citet{2015ApJ...806L..28S}), which is a three-parameter potential-density pair, whose quantities such as density, potential, and binding energy can be written in closed form.  The galaxies were evolved from $4 > z > 0$.  Orbiting black holes were periodically introduced into the "host" galaxy and their dynamical interaction with the background potential and central SMBH were followed, as described further below.
